---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# savonliquide

<!-- badges: start -->
<!-- badges: end -->


`savonliquide` allows you to generate a report from the [Contrast Checker API](https://webaim.org/resources/contrastchecker/). The report will display a contrast ratio (that should be above a threshold among) other useful information that will judge the accessibility level of your colors contrast.

## Installation

You can install the released version of `savonliquide` from [CRAN](https://CRAN.R-project.org) with:


```{r, eval=FALSE}

remotes::install_github("feddelegrand7/savonliquide")

```


## Example


The following plot is awful in terms of color contrast. The two main colors used are : `#FDF6E3` (for points) and `#C6F6E3"` for the background.

```{r}

library(ggplot2)

ggplot(mpg, aes(hwy, cty)) +
  geom_point(color = "#FDF6E3") +
  theme(panel.background = element_rect(fill = "#C6F6E3"))



```


Let's check the contrast: 


```{r}
library(savonliquide)
# fg_col stands for foreground color 
# bg_col stands for background color


check_contrast(fg_col = "#FDF6E3", 
               bg_col = "#C6F6E3")


```

You can see that the report indicates that we've a very low Contrast Ratio and that we've failed all the recommended standards (In the web development industry we consider mostly the AA standard). 


Now let's experiment other colors combinations. Let's go for: 

+ Foreground color: #0000FF

+ Background color: #FFFFFF


```{r}

check_contrast(fg_col = "#0000FF", 
               bg_col = "#FFFFFF")


```
Awesome ! we've got an excellent Contrast Ratio and we've passed all the accessibility standards. Let's use the above colors to render our plot again: 


```{r}

ggplot(mpg, aes(hwy, cty)) +
  geom_point(color = "#0000FF") +
  theme(panel.background = element_rect(fill = "#FFFFFF"))



```

## Code of Conduct

Please note that the savonliquide project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
